High Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogenous Catalysis in Higly Sensitive Microreactors

### 2012-03-27 paper.tex
Changes before Robert's first readthrough

\author{T. Andersen}
\author{R. Jensen}
\author{....}
\affiliation{CINF, Department of Physics...}
\author{O. Hansen}
\affiliation{CINF, Department of Micro- and Nanotechnology}
\author{I. Chorkendorff}
\email[]{ibchork@fysik.dtu.dk}
\affiliation{CINF, Department of Physics...}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
%\affiliation{}

@@

\begin{abstract}
We demonstrate a combined microreactor and time of flight system for testing and characterization of heterogeneous catalyst with high resolution mass spectrometry and high sensitivity. Catalyst testing is performed in microreactors which have high sensitivity and fast thermal response. Gas analysis is performed with a time of flight mass spectrometer with a modified nude Bayard-Alpert ionization gauge as gas ionization source with a mass resolution of $\Delta$m/m$>$2500. The system design is superior to conventional batch and flow reactors not only due to the high sensitivity, fast temperature response and high mass resolution but also allows to measure on wide mass ranges (0--5000\,amu in the current configuration). As demonstration of the system we here present data from ammonia oxidation on platinum thin films showing resolved spectra of OH$^{-}$ and NH$_{3}^{+}$.
\end{abstract}

@@

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
In heterogeneous catalysis the optimization and development of equipment is important both to minimize the cost of equipment but also to be able to study complicated systems. As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients. Such a platform have been developed in our department \cite{Henriksen2009}. However, a suitable reactor platform is only part of the task; reactant and product detection and characterization is essential to determine catalyst performance. Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs are used for high pressure measurements. The QMS, however, suffer from a low mass resolution ($\Delta$m/m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome. The QMS is additionally subject to a low mass range (typically up to $\sim$500\,amu) limiting general use. Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase the time resolution. This in turn limits the ability to acquire full mass spectra continuously during the experiment. Gas chromatographs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers. As an alternative to the gas chromatography or QMSs, time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$400) and fast acquisition of full mass spectra ($>$1\,Hz) along with mass range only limited by the detector. For a typical microchannel plate (MCP) a mass range of (0--5000\,amu) can be obtained. Until now, to our knowledge, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS have not been demonstrated. Here we describe a microreactor and TOF-MS system which combines the high sensitivity of microreactors and the high mass resolution TOF-MSs for testing and characterizing heterogeneous catalysts.

@@

\subsection{Microreactor and gas handling}

@@

\subsubsection{Gas handling}
The two gas inlets on the microreactor chip is connected to a gas handling system. A total of 6 gases with accompanying flow controllers are used to control the inlet gas flow to the microreactor. Currently, the system is configured in a 4+2 setup where 4 gases are connected to the one inlet and to gases on the other inlet. All valves and flow controllers are interfaced to computer enabling remote control of the system and the possibility to run experiments over several days without human intervention.

@@

\subsubsection{Data treatment}
A raw data plotted with accompanying gaussian fits are shown in Figure \ref{fig:gaussian_fit}.
\begin{figure}
 \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
 \caption{Example of two gaussian fits to a double peak consisting of NH$_{3}^{+}$ and OH$^{-}$ both at approximately 17\,amu demonstrating the resolution of the TOF-MS. The entire graph section represents a mass difference of 100\,m-amu.\label{fig:gaussian_fit}}%
\end{figure}
The TOF-MS has furthermore the advantage of a high dynamic range compared to eg. a QMS. In Figure \ref{fig:dynamic_range} raw data from water, hydrogen and oxygen is shown. Without changing any the MCP voltage all the peaks are clearly visible although the ratio of the oxygen to water amplitude is roughly a factor of 4000. 
\begin{figure}
 \includegraphics[width=14cm]{dynamic_range.png}%
 \caption{Gaussian fits to three different mass to charge ratios from the same mass spectrum. As seen from the response a high dynamic range of the TOF-MS all yielding good gaussian fits. The TOF-MS can hence be used to monitor both very small and very large signal masses with high time resolution.\label{fig:dynamic_range}}%
\end{figure}

\section{Oxidation of ammonia}
To demonstrate the system capability ammonia oxidation on platinum thin films has been used as test reaction. The catalytic oxidation of ammonia can proceed along primarily three different routes.
\begin{equation}
4NH_3+3O_2\rightarrow 2N_2 + 6H_2O
\label{eq:Pt_clean_combustion}
\end{equation}
\begin{equation}
2NH_3+2O_2\rightarrow N_2O + 3H_2O
\end{equation}
\begin{equation}
4NH_3+5O_2\rightarrow 4NO + 6H_2O
\end{equation}
All of these systems are difficult to analyze both qualitatively and quantitatively by a QMS due to the overlap of NH$_3$, which is a reactant, and OH$^-$ which is a cracking product from H$_2$O, which is a product from the combustion. Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at m/q$\simeq$17 in a QMS. The low mass resolution of a QMS is typically not adequate to separate the two contributions resulting i difficult analysis. Often a charge to mass ratio without cracking from either products or residue gas in the system is used to be able to detect the amount of ammonia and water. In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen. The monitoring of other than the primary mass to charge ratio due to mass overlap is generally not wanted due to a lower signal to noise ratio of cracking masses. This in turns affect the detection limit of the given mass. Due the acquisition of entire mass spectra with high time resolution instead of monitoring individual masses by QMS the TOF-MS is not limited to unique signature masses resulting in higher signal to noise ratio spectra.
\begin{figure}
 \includegraphics[width=14cm]{ammonia_reactivity.png}%
 \caption{Ammonia oxidation as a function of temperature on a Pt thin film. As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$. Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these masses.\label{fig:ammonia_reactivity}}%
\end{figure}
In Figure \ref{fig:ammonia_reactivity} a number of masses as a function of time are shown. At experiment start the microreactor is equilibrated with a stoichiometric mix of NH$_3$ and O$_2$ (3:4). Hereafter the temperature is increased while TOF spectra are acquired. Spectra were acquired from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to a maximum of 70 amu in our system.

For ammonia oxidation both N$_2$O (m/q = 44), NO (m/q = 30) and NO$_2$ (m/q = 46) are of interest.

\section{Summary}

@@

% Create the reference section using BibTeX:
\bibliographystyle{abbrv}
%\bibliographystyle{alpha}
%\bibliographystyle{plain}
\bibliography{literature}

>>>>

\author{T. Andersen}
\author{R. Jensen}
\author{....}
\affiliation{Department of Physics, Danish National Research Foundation's Center for Individual Nanoparticle Functionality (CINF), Technical University of Denmark, Building 312, DK-2800 Kgs. Lyngby, Denmark}
\author{O. Hansen}
\affiliation{Department of Micro- and Nanotechnology, Technical University of Denmark, DTU Nanotech Building 345 East, DK-2800 Kgs. Lyngby, Denmark}
\author{I. Chorkendorff}
\email[]{ibchork@fysik.dtu.dk}
\affiliation{Department of Physics, Danish National Research Foundation's Center for Individual Nanoparticle Functionality (CINF), Technical University of Denmark, Building 312, DK-2800 Kgs. Lyngby, Denmark}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
%\affiliation{}

@@

\begin{abstract}
We demonstrate a combined microreactor and time of flight system for testing and characterization of heterogeneous catalyst with high resolution mass spectrometry and high sensitivity. Catalyst testing is performed in microreactors which have high sensitivity and fast thermal response. Gas analysis is performed with a time of flight mass spectrometer with a modified nude Bayard-Alpert ionization gauge as gas ionization source with a mass resolution of $\Delta$m/m$>$2500. The system design is superior to conventional batch and flow reactors not only due to the high sensitivity, fast temperature response and high mass resolution but also allows to measure on wide mass ranges (0--5000\,amu in the current configuration). As demonstration of the system we here present data from ammonia oxidation on platinum thin films showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
\end{abstract}

@@

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
In heterogeneous catalysis the optimization and development of equipment is important both to minimize the cost of equipment but also to be able to study complicated systems. As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients. Such a platform have been developed in our department \cite{Henriksen2009}. However, a suitable reactor platform is only part of the task; reactant and product detection and characterization is essential to determine catalyst performance. Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs are used for high pressure measurements. The QMS, however, suffer from a low mass resolution ($\Delta$m/m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome. The QMS is additionally subject to a low mass range (typically up to $\sim$500\,amu) limiting general use. Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution. This in turn limits the ability to acquire full mass spectra continuously during the experiment. Gas chromatographs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers. As an alternative to the gas chromatography or QMSs, time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$400) and fast acquisition of full mass spectra ($>$1\,Hz) along with mass range only limited by the detector. For a typical microchannel plate (MCP) a mass range of (0--5000\,amu) can be obtained. Until now, to our knowledge, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS have not been demonstrated. Here we describe a microreactor and TOF-MS system which combines the high sensitivity of microreactors and the high mass resolution TOF-MSs for testing and characterizing heterogeneous catalysts.

@@

@@

\subsubsection{Gas handling for the microreactor}
The two gas inlets on the microreactor chip is connected to a gas handling system. A total of 6 gases with accompanying flow controllers are used to control the inlet gas flow to the microreactor. Currently, the system is configured in a 4+2 setup where 4 gases are connected to the one inlet and to gases on the other inlet. All valves and flow controllers are interfaced to computer enabling remote control of the system and the possibility to run experiments over several days without human intervention.

@@

\subsubsection{Data treatment}
Raw data plotted with accompanying gaussian fits are shown in Figure \ref{fig:gaussian_fit}. Here the closely lying peaks from OH$^{+}$ from cracking of both residue water and water as reaction product and uncombusted NH$_3^{+}$ is shown. The ability to separate these contributions substantially simplifies quantification of the ammonia and allows for easier characterization of catalysts. 
\begin{figure}
 \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
 \caption{Example of two gaussian fits to a double peak consisting of NH$_{3}^{+}$ and OH$^{+}$ both at approximately 17\,amu demonstrating the resolution of the TOF-MS. The entire graph section represents a mass difference of 100\,m-amu.\label{fig:gaussian_fit}}%
\end{figure}
In Figure \ref{fig:dynamic_range} raw data from water, hydrogen and oxygen from three different regions is shown illustrating the dynamic range of the TOF-MS. At constant MCP voltage all the peaks are clearly visible although the ratio of the oxygen to water amplitude is $\sim$400. 
\begin{figure}
 \includegraphics[width=14cm]{dynamic_range.png}%
 \caption{Gaussian fits to three different mass to charge ratios from the same mass spectrum. As seen from the response a high dynamic range of the TOF-MS all yielding good gaussian fits. The TOF-MS can hence be used to monitor both very small and very large signal masses with high time resolution.\label{fig:dynamic_range}}%
\end{figure}
The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range. From Figure \ref{fig:dynamic_range} the dynamic range is estimated to $\sim$1000. Her ville jeg gerne skrive noget mere. Nogen ideer...?

\section{Oxidation of ammonia}
To demonstrate the system capability ammonia oxidation on platinum thin films has been used as test reaction. The catalytic oxidation of ammonia can proceed along primarily three different routes.
\begin{equation}
4NH_3+3O_2\rightarrow 2N_2 + 6H_2O
\label{eq:Pt_clean_combustion}
\end{equation}
\begin{equation}
2NH_3+2O_2\rightarrow N_2O + 3H_2O
\end{equation}
\begin{equation}
4NH_3+5O_2\rightarrow 4NO + 6H_2O
\end{equation}
All of these systems are difficult to analyze both qualitatively and quantitatively by due to the overlap of NH$_3$, which is a reactant, and OH$^+$ originating from cracking of H$_2$O, which is a product from the combustion, and cracking from water in the residue gas. Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at m/q$\simeq$17. Without adequate mass resolution is not possible to separate the two contributions resulting in difficult analysis. Often a charge to mass ratio without cracking from either products or residue gas in the system is used to quantify the amount of ammonia and water. In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen. The monitoring of other than the primary mass to charge ratio, which in the case of ammonia is m/q=17, due to mass overlap is generally not wanted due to a lower signal to noise ratio of cracking masses. This in turns affect the detection limit of the given mass. Due the acquisition of entire mass spectra with high mass resolution instead of monitoring individual masses by the TOF-MS is not limited to unique signature masses resulting in higher signal to noise ratio spectra.

At experiment start the microreactor is equilibrated with NH$_3$ and O$_2$ in a 5:3 stoichiometry (did we run at stoichiometry??). After equilibration the temperature is increased in steps from room temperature til 190\,$^{\circ}$C. The gas composition in the microreactor is continuously probed by the TOF-MS which is connected to the capillary of the microreactor.
\begin{figure}
 \includegraphics[width=14cm]{ammonia_reactivity.png}%
 \caption{Ammonia oxidation as a function of temperature on a Pt thin film. As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$. Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these two close lying masses.\label{fig:ammonia_reactivity}}%
\end{figure}
In Figure \ref{fig:ammonia_reactivity} the integrated N$_2$, NH$_3$, H$_2$O, O$_2$ and OH peaks acquired from the raw TOF-MS spectrum as a function of temperature are shown. At each individual temperature step a mass scan is performed from the triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to a maximum of 70 amu. As seen from Figure \ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 140\,$^{\circ}$C. The combustion of ammonia to molecular nitrogen and water at this temperature agrees well with literature \cite{Imbihl2007,Zeng2009}. In Figure \ref{fig:ammonia_reactivity} an anticorrelation between OH$^{+}$ and NH$_3^+$ is seen. The inverse relation between these two masses suggests that these peaks are resolved in the mass spectrum which is further strengthened by the correlation between H$_2$O$^{+}$.

%For ammonia oxidation both N$_2$O (m/q = 44), NO (m/q = 30) and NO$_2$ (m/q = 46) are of interest.

\section{Summary}
We have demonstrated a combined microreactor and TOF-MS system which can be employed to test and characterize model heterogeneous catalysts. An automated gas handling system is used to flow gas over a catalyst in the reaction chamber of the microreactor from where gases can be probed. The reactor gas composition is probed by a microreactor capillary which is analyzed by a TOF-MS combining high sensitivity and high mass resolution.

As a demonstration of the system ammonia oxidation on platinum thin films was performed. The ability to resolve OH$^{+}$ and NH$_3^+$ was demonstrated which is separated by 23\,milli-amu. The resolution of reactants and products enables simple and straightforward quantification of the ammonia and water signal. This greatly simplifies the analysis compared to conventional QMSs used for gas analysis. The setup is furthermore superior to conventional QMSs where the mass range is limited to $\sim$500\,amu.

@@

% Create the reference section using BibTeX:
%\bibliographystyle{abbrv}
%\bibliographystyle{alpha}
%\bibliographystyle{plain}
%\bibliographystyle{unsrt}
\bibliography{literature}
